---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

R functions for creating square and hextile maps for various countries (only USA for now). 

## Installation

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/tilemapr")
library(tilemapr)
```

## Usage

Tile grid maps are good alternative when the population isn't of much interest. Below we see a minimal example using ggplot2 and `geom_map()`:

```{r}
library(ggplot2)

# Creating data
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
states_map <- square_usa()

ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = states_map) +
  expand_limits(x = states_map$long, y = states_map$lat)
```

All the functions include a number of parameters to control the resulting data.frame. The two most important ones are the `d` and `center`. `d` is a kind of diameter parameter which is used to control the size of the tiles. And `center` make the function gives us a data.frame with the coordinates of the center of the tile.

```{r}
states_map <- hex_usa(d = 0.5)

ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = states_map) +
  expand_limits(x = states_map$long, y = states_map$lat) +
  geom_text(data = hex_usa(d = 0.5, center = TRUE), 
            aes(x = long, y = lat, label = states_abb), 
            inherit.aes = FALSE)
```

We see here that DC is floating, this will be a common issue. It can be resolved by either removing it with `exclude` or to plotting a dataless map underneath:

```{r}
states_map <- hex_usa(d = 0.5)

ggplot(states_map, aes(map_id = region)) +
  geom_map(aes(), map = states_map) +
  geom_map(data = crimes, map = states_map,
           aes(fill = Murder, map_id = state)) +
  expand_limits(x = states_map$long, y = states_map$lat) +
  geom_text(data = hex_usa(d = 0.5, center = TRUE), 
            aes(x = long, y = lat, label = states_abb), 
            inherit.aes = FALSE)
```

Lastly some of the functions have different layout, which are picked using the `style`.

```{r, echo=FALSE}
library(gridExtra)

states_map <- square_usa(style = "The Guardian")

q1 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "NPR")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "NPR") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q2 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "The New York Times")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "The New York Times") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q3 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "538")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "538") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q4 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "Propublica")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "Propublica") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q5 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "Bloomberg")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "Bloomberg") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q6 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "The Guardian")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "The Guardian") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q7 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "Wall Street Journal")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "Wall Street Journal") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q8 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "WNYC")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "WNYC") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)
q9 <- ggplot(crimes, aes(map_id = state)) +
  geom_map(aes(fill = Murder), map = square_usa(style = "The Marshall Project")) +
  expand_limits(x = c(-1, 13), y = c(-2, 9)) +
  labs(title = "The Marshall Project") + 
  guides(fill = "none") +
  theme_void() + 
  coord_fixed(ratio = 1)

grid.arrange(q1, q2, q3, q4, q5, q6, q7, q8, q9, ncol = 3, nrow = 3)
```


